### 2024-09-24 paper/paper.qmd
Add files via upload

---
title: "Marriage Data analysis"
subtitle: "STA304 WEEK 3"
author: 
  - Maggie Zhang
thanks: "Code and data are available at:https://github.com/MaggieZ111119/marriage.git"
date: today
date-format: long
abstract: "This is an analysis study on marriage data set in from Toronto. The goal is to examine the impact of marriage on influencing the social and financial status of individuals. The result carrying out supporting roles for sustainability improvements, financial support, public policy forming, etc."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)

# Read Data(Quarto need dataset to be readed in the file)
data <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))
```

# Introduction

The Data are extracted from @OpenDataToronto, learn and used @citeR and @rohan.

# Data {#sec-data}

# Results
This histogram (@fig-marriagedata) reflects the amount new marriage happens each year from the year of 2011 to 2024 according to @OpenDataToronto.

```{r}
#| label: fig-marriagedata
#| fig-cap: Marriage
#| echo: false

ggplot(data = data, 
       aes(x = year, y = marriage_licenses)) +
  geom_bar(stat = "identity") + labs(title = "Amount New Marriage Each Year 2011 - 2024", x = "Year", y = "Marriage Number")
```

# Discussion

## First discussion point {#sec-first-point}

from the study, the Marriage number across Toronto is .....

## Second discussion point

[My second point]

## Third discussion point
[My third point]

## Weaknesses and next steps

The study is not finalized, more detailed and careful data examination is needed.

\newpage

\appendix

# Appendix {-}

# References

### 2024-09-24 scripts/00-simulate_data.R
test

@@ -7,7 +7,7 @@
 # Pre-requisites: First sketch the idea of 
 # Any other information needed? Not much
 
-set.seed(304)
+set.seed(1009633096)
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-09-24 scripts/01-download_data.R

@@ -13,6 +13,8 @@ library(opendatatoronto)
 library(tidyverse)
 
 #### Download data ####
+
+
 raw_marriage_data <-
   read_csv(
     file = "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/e28bc818-43d5-43f7-b5d9-bdfb4eda5feb/resource/01dff98a-b56b-4237-bb5d-f56319f0ced6/download/Marriage%20Licence%20Statistics%20Data.csv",

### 2024-09-24 scripts/01-download_data.R
download data(2020,2019,2018,2017)

@@ -11,21 +11,45 @@
 #### Workspace setup ####
 library(opendatatoronto)
 library(tidyverse)
+library(dprly)
 
 #### Download data ####
 
+### Shelter occupancy 2020 ###
+#Downloaded data for Shelter occupancy in the year 2020 from OpenDataToronto as csv. file
 
-raw_marriage_data <-
-  read_csv(
-    file = "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/e28bc818-43d5-43f7-b5d9-bdfb4eda5feb/resource/01dff98a-b56b-4237-bb5d-f56319f0ced6/download/Marriage%20Licence%20Statistics%20Data.csv",
-    show_col_types = FALSE
-  )
+raw_2020_shelter <- read_csv(file = "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/8a6eceb2-821b-4961-a29d-758f3087732d/resource/9e076fe4-2f86-48d7-a6e4-93710ca715ae/download/Daily%20shelter%20occupancy%202020.csv",
+                             show_col_types = FALSE)
+#Save Data
+write_csv(raw_2020_shelter, 
+          "data/raw_data/raw_2020_shelter_data.csv") 
 
 
+### Shelter occupancy 2019 ###
+#Downloaded data for Shelter occupancy in the year 2019 from OpenDataToronto as csv. file
 
-#### Save data ####
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(raw_marriage_data, 
-          "starter_folder-main/data/raw_data/raw_marriage_data.csv") 
+raw_2019_shelter <- read_csv(file = "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/8a6eceb2-821b-4961-a29d-758f3087732d/resource/3ea9d9ba-f05f-4055-bcc3-333f699c5e77/download/Daily%20shelter%20occupancy%202019.csv",
+                             show_col_types = FALSE)
+#Save Data
+write_csv(raw_2019_shelter, 
+          "data/raw_data/raw_2019_shelter_data.csv") 
 
-         
+
+### Shelter occupancy 2018 ###
+#Downloaded data for Shelter occupancy in the year 2018 from OpenDataToronto as csv. file
+
[…]

### 2024-09-24 scripts/01-download_data.R
clear unused pakages

@@ -11,7 +11,6 @@
 #### Workspace setup ####
 library(opendatatoronto)
 library(tidyverse)
-library(dprly)
 
 #### Download data ####
 

### 2024-09-24 scripts/02-data_cleaning.R
Data Cleaning (select intrested columns, creating columns contains useful information, and fixing format)

@@ -9,10 +9,64 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
 
 #### Clean data ####
-raw_marriage_data <- read_csv(
-  "starter_folder-main/data/raw_data/raw_marriage_data.csv")
+raw_2017_shelter <- data.frame(read_csv(
+  "data/raw_data/raw_2017_shelter_data.csv", show_col_types = FALSE))
+raw_2018_shelter <- data.frame(read_csv(
+  "data/raw_data/raw_2018_shelter_data.csv", show_col_types = FALSE))
+raw_2019_shelter <- data.frame(read_csv(
+  "data/raw_data/raw_2019_shelter_data.csv", show_col_types = FALSE))
+raw_2020_shelter <- data.frame(read_csv(
+  "data/raw_data/raw_2020_shelter_data.csv", show_col_types = FALSE))
+
+
+## Fix issue with data in four dataset, and select columns within our interest.
+#2017 Data
+cleaned_2017 <- raw_2017_shelter %>%
+  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
+  summarize(
+    Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
+    Totoal_Capacity = sum(CAPACITY, na.rm = TRUE),
+    .groups = 'drop') %>%
+  select(OCCUPANCY_DATE, SHELTER_CITY, SECTOR, 
+         Totoal_Occupancy, Totoal_Capacity)
+
+#2018 Data
+cleaned_2018 <- raw_2018_shelter %>%
+  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
+  summarize(
+    Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
+    Totoal_Capacity = sum(CAPACITY, na.rm = TRUE),
+    .groups = 'drop') %>%
+  select(OCCUPANCY_DATE, SHELTER_CITY, SECTOR, 
+         Totoal_Occupancy, Totoal_Capacity)
+
+#2019 Data
+cleaned_2019 <- raw_2019_shelter %>%
+  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
+  summarize(
+    Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
[…]

### 2024-09-24 scripts/02-data_cleaning.R
Furthur adjust the format of date, and combine the dataset for 4 years for easier analysis.

@@ -25,6 +25,7 @@ raw_2020_shelter <- data.frame(read_csv(
 ## Fix issue with data in four dataset, and select columns within our interest.
 #2017 Data
 cleaned_2017 <- raw_2017_shelter %>%
+  mutate(date = as.Date(raw_2017_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) %>%
   group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
   summarize(
     Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
@@ -32,9 +33,13 @@ cleaned_2017 <- raw_2017_shelter %>%
     .groups = 'drop') %>%
   select(OCCUPANCY_DATE, SHELTER_CITY, SECTOR, 
          Totoal_Occupancy, Totoal_Capacity)
+cleaned_2017$OCCUPANCY_DATE <-  as.Date(cleaned_2017$OCCUPANCY_DATE, 
+                                        as.is = double, na.rm = TRUE)
+
 
 #2018 Data
 cleaned_2018 <- raw_2018_shelter %>%
+  mutate(date = as.Date(raw_2018_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) %>%
   group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
   summarize(
     Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
@@ -42,9 +47,12 @@ cleaned_2018 <- raw_2018_shelter %>%
     .groups = 'drop') %>%
   select(OCCUPANCY_DATE, SHELTER_CITY, SECTOR, 
          Totoal_Occupancy, Totoal_Capacity)
+cleaned_2018$OCCUPANCY_DATE <-  as.Date(cleaned_2018$OCCUPANCY_DATE, 
+                                        as.is = double, na.rm = TRUE)
 
 #2019 Data
 cleaned_2019 <- raw_2019_shelter %>%
+  mutate(date = as.Date(raw_2019_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) %>%
   group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
   summarize(
     Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
@@ -52,6 +60,8 @@ cleaned_2019 <- raw_2019_shelter %>%
     .groups = 'drop') %>%
[…]

### 2024-09-24 scripts/00-simulate_data.R
Further sadjust the simulation to better capture the dataset. Also developed some tests.

@@ -12,19 +12,51 @@ set.seed(1009633096)
 #### Workspace setup ####
 library(tidyverse)
 
-start_data <- as.Date("2018-01-01")
-end_date <- as.Date("2023-12-31")
+## Since the dataset contains information that is not in my intrest and will not effect my understanding of my intrest. I will later remove them in the data selection section, thus, I'm not going to be simulated information about these colum (eg. PROGRAM_NAME, FACILITY_NAME, etc.)
+
 
 #### Simulate data ####
-number_of_date <- 100
 
-data <-
-  tibble(
-    date = as.Date(runif(n = number_of_date, 
-                         min = as.numeric(start_data), 
-                         max = as.numeric(end_date))),
-    number_of_marriage = rpois(n = num_of_date, lambda = 10)
-  )
+## Date of data collection
+#Since the date in the data are collected each day at 4:00 am.
+start_data <- as.Date("2017-01-01")
+end_date <- as.Date("2020-12-31")
+Date_seq = seq(from = start_data, to = end_date, by = "day")
+Date <- rep(Date_seq, each = 4)
+
+
+## The City of shelter
+# Randomly pick a city to locate the shelter from all cities that has shelters suggested by the dataset from 2017 to 2020.
+appeared_city = unique(c(unique(raw_2017_shelter$SHELTER_CITY), 
+              unique(raw_2018_shelter$SHELTER_CITY),
+              unique(raw_2019_shelter$SHELTER_CITY),
+              unique(raw_2020_shelter$SHELTER_CITY)
+              ))
+City = sample(appeared_city, size = length(Date), replace = TRUE)
+
+## The Province of shelter
+# Randomly pick a city to locate the shelter from all provinces that has shelters suggested by the dataset from 2017 to 2020.
+appeared_province = unique(c(unique(raw_2017_shelter$SHELTER_PROVINCE), 
+                         unique(raw_2018_shelter$SHELTER_PROVINCE),
+                         unique(raw_2019_shelter$SHELTER_PROVINCE),
+                         unique(raw_2020_shelter$SHELTER_PROVINCE)
+                         ))
+Province = sample(appeared_province, size = length(Date), replace = TRUE)
+
+
+
+## The amount each sector occupying the shelter, group by Cities
+# Randomly pick a type of Sector who is using the shelter from all Sectors exist within our focus suggested by the dataset from 2017 to 2020.
[…]

### 2024-09-24 scripts/02-data_cleaning.R
Stored the cleaned data into the data file

@@ -85,4 +85,4 @@ head(full_shelter_data)
 tail(full_shelter_data)
 
 #### Save data ####
-write_csv(cleaned_data, "starter_folder-main/data/analysis_data/cleaned_data.csv")
+write_csv(full_shelter_data, "data/analysis_data/full_shelter_data.csv")

### 2024-09-24 scripts/00-simulate_data.R
Change a more meaningful name to the simulated data. And deleted unused files

@@ -7,7 +7,6 @@
 # Pre-requisites: First sketch the idea of 
 # Any other information needed? Not much
 
-set.seed(1009633096)
 
 #### Workspace setup ####
 library(tidyverse)
@@ -18,45 +17,92 @@ library(tidyverse)
 #### Simulate data ####
 
 ## Date of data collection
-#Since the date in the data are collected each day at 4:00 am.
+set.seed(1009633096)
 start_data <- as.Date("2017-01-01")
 end_date <- as.Date("2020-12-31")
-Date_seq = seq(from = start_data, to = end_date, by = "day")
-Date <- rep(Date_seq, each = 4)
+Date_seq = seq(from = start_data, to = end_date, by = "day") %>% as.character()
 
 
 ## The City of shelter
-# Randomly pick a city to locate the shelter from all cities that has shelters suggested by the dataset from 2017 to 2020.
-appeared_city = unique(c(unique(raw_2017_shelter$SHELTER_CITY), 
+appeared_city <-  unique(c(unique(raw_2017_shelter$SHELTER_CITY), 
               unique(raw_2018_shelter$SHELTER_CITY),
               unique(raw_2019_shelter$SHELTER_CITY),
               unique(raw_2020_shelter$SHELTER_CITY)
               ))
-City = sample(appeared_city, size = length(Date), replace = TRUE)
 
-## The Province of shelter
-# Randomly pick a city to locate the shelter from all provinces that has shelters suggested by the dataset from 2017 to 2020.
-appeared_province = unique(c(unique(raw_2017_shelter$SHELTER_PROVINCE), 
-                         unique(raw_2018_shelter$SHELTER_PROVINCE),
-                         unique(raw_2019_shelter$SHELTER_PROVINCE),
-                         unique(raw_2020_shelter$SHELTER_PROVINCE)
-                         ))
-Province = sample(appeared_province, size = length(Date), replace = TRUE)
+
+# All involved sector categories:
+sectors <- c("women", "men", "youth", "co-ed", "family")
 
 
 
-## The amount each sector occupying the shelter, group by Cities
-# Randomly pick a type of Sector who is using the shelter from all Sectors exist within our focus suggested by the dataset from 2017 to 2020.
-appeared_sectors = unique(c(unique(raw_2017_shelter$SECTOR), 
-                             unique(raw_2018_shelter$SECTOR),
[…]

### 2024-09-26 scripts/00-simulate_data.R
Move test code for simulated data to test script

@@ -81,28 +81,5 @@ for (date in Date_seq) {
 # head(simulated_dataset)
 
 
-## TEST1: Missing Value
-num_missing_values <- sum(is.na(simulated_dataset))
-cat("Total missing values: ", num_missing_values, "\n")
-
-
-## TEST2: Negative value (Total_Occupancy and Total_Capacity)
-negative_occupancy <- sum(simulated_dataset$Total_Occupancy < 0)
-negative_capacity <- sum(simulated_dataset$Total_Capacity < 0)
-cat("Total negative occupancy values: ", negative_occupancy, "\n")
-cat("Total negative capacity values: ", negative_capacity, "\n")
-
-
-## TEST3: Date Format is consistent
-incorrect_dates <- sum(!grepl("^\\d{4}-\\d{2}-\\d{2}$", simulated_dataset$OCCUPANCY_DATE))
-
-if (incorrect_dates > 0) {
-  message("Warning: ", incorrect_dates, " dates are not in the correct format (YYYY-MM-DD).")
-} else {
-  message("All dates are in the correct format (YYYY-MM-DD).")
-}
-
-
-
 # Write and store the simulated dataset
 write_csv(simulated_dataset, file = "data/raw_data/simulated_dataset_shelter_data.csv")

### 2024-09-26 scripts/03-test_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Test and check of the simulated data
 # Author: Maggie Zhang
-# Date: 19 September 2024
+# Date: 26 September 2024
 # Contact: maggiey.zhang@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: have the data ready into R
@@ -13,11 +13,27 @@ library(tidyverse)
 
 
 #### Test data ####
-data <- read.csv("starter_folder-main/data/raw_data/simulated.csv")
-
-# Test for Neg
-data$number_of_marriage |> min() <= 0
+simulated_dataset <- read.csv("data/raw_data/simulated_dataset_shelter_data.csv")
 
 
-# Test for NAs
-all(is.na(data$number_of_marriage))
+## TEST1: Missing Value
+num_missing_values <- sum(is.na(simulated_dataset))
+cat("Total missing values: ", num_missing_values, "\n")
+
+
+## TEST2: Negative value (Total_Occupancy and Total_Capacity)
+negative_occupancy <- sum(simulated_dataset$Total_Occupancy < 0)
+negative_capacity <- sum(simulated_dataset$Total_Capacity < 0)
+cat("Total negative occupancy values: ", negative_occupancy, "\n")
+cat("Total negative capacity values: ", negative_capacity, "\n")
+
+
+## TEST3: Date Format is consistent
+incorrect_dates <- sum(!grepl("^\\d{4}-\\d{2}-\\d{2}$", simulated_dataset$OCCUPANCY_DATE))
+
+if (incorrect_dates > 0) {
+  message("Warning: ", incorrect_dates, " dates are not in the correct format (YYYY-MM-DD).")
+} else {
+  message("All dates are in the correct format (YYYY-MM-DD).")
+}
+

### 2024-09-26 scripts/00-simulate_data.R
Replace %>% by |>

@@ -20,7 +20,7 @@ library(tidyverse)
 set.seed(1009633096)
 start_data <- as.Date("2017-01-01")
 end_date <- as.Date("2020-12-31")
-Date_seq = seq(from = start_data, to = end_date, by = "day") %>% as.character()
+Date_seq = seq(from = start_data, to = end_date, by = "day") |> as.character()
 
 
 ## The City of shelter

### 2024-09-26 scripts/02-data_cleaning.R

@@ -24,13 +24,13 @@ raw_2020_shelter <- data.frame(read_csv(
 
 ## Fix issue with data in four dataset, and select columns within our interest.
 #2017 Data
-cleaned_2017 <- raw_2017_shelter %>%
-  mutate(date = as.Date(raw_2017_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) %>%
-  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
+cleaned_2017 <- raw_2017_shelter |>
+  mutate(date = as.Date(raw_2017_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) |>
+  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) |> 
   summarize(
     Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
     Totoal_Capacity = sum(CAPACITY, na.rm = TRUE),
-    .groups = 'drop') %>%
+    .groups = 'drop') |>
   select(OCCUPANCY_DATE, SHELTER_CITY, SECTOR, 
          Totoal_Occupancy, Totoal_Capacity)
 cleaned_2017$OCCUPANCY_DATE <-  as.Date(cleaned_2017$OCCUPANCY_DATE, 
@@ -38,38 +38,38 @@ cleaned_2017$OCCUPANCY_DATE <-  as.Date(cleaned_2017$OCCUPANCY_DATE,
 
 
 #2018 Data
-cleaned_2018 <- raw_2018_shelter %>%
-  mutate(date = as.Date(raw_2018_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) %>%
-  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) %>% 
+cleaned_2018 <- raw_2018_shelter |>
+  mutate(date = as.Date(raw_2018_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) |>
+  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) |> 
   summarize(
     Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
     Totoal_Capacity = sum(CAPACITY, na.rm = TRUE),
-    .groups = 'drop') %>%
+    .groups = 'drop') |>
   select(OCCUPANCY_DATE, SHELTER_CITY, SECTOR, 
[…]

### 2024-09-26 scripts/02-data_cleaning.R
Clean names of columns, make them consistent

@@ -25,55 +25,97 @@ raw_2020_shelter <- data.frame(read_csv(
 ## Fix issue with data in four dataset, and select columns within our interest.
 #2017 Data
 cleaned_2017 <- raw_2017_shelter |>
-  mutate(date = as.Date(raw_2017_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) |>
-  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) |> 
+  # clean names of columns 
+  janitor::clean_names() |>
+  # change date to recognizable format
+  mutate(date = as.Date(raw_2017_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d"))
+
+cleaned_2017 <- cleaned_2017 |>
+  # get information needed for analysis with my interest
+  group_by(occupancy_date,shelter_city,sector) |> 
   summarize(
-    Totoal_Occupancy = sum(OCCUPANCY, na.rm = TRUE),
-    Totoal_Capacity = sum(CAPACITY, na.rm = TRUE),
+    # occupancy number in each city for each sector 
+    totoal_occupancy = sum(occupancy, na.rm = TRUE),
+    # occupancy number in each city for each sector 
+    totoal_capacity = sum(capacity, na.rm = TRUE),
     .groups = 'drop') |>
-  select(OCCUPANCY_DATE, SHELTER_CITY, SECTOR, 
-         Totoal_Occupancy, Totoal_Capacity)
-cleaned_2017$OCCUPANCY_DATE <-  as.Date(cleaned_2017$OCCUPANCY_DATE, 
+  select(occupancy_date, shelter_city, sector, 
+         totoal_occupancy, totoal_capacity)
+
+# Make sure date format is consistent with other three datasets
+cleaned_2017$occupancy_date <-  as.Date(cleaned_2017$occupancy_date, 
                                         as.is = double, na.rm = TRUE)
 
 
 #2018 Data
 cleaned_2018 <- raw_2018_shelter |>
-  mutate(date = as.Date(raw_2018_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d")) |>
-  group_by(OCCUPANCY_DATE,SHELTER_CITY,SECTOR) |> 
+  # clean names of columns 
+  janitor::clean_names() |>
+  # change date to recognizable format
+  mutate(date = as.Date(raw_2018_shelter$OCCUPANCY_DATE, format = "%Y-%m-%d"))
+
+cleaned_2018 <- cleaned_2018 |>
[…]

### 2024-09-26 scripts/00-simulate_data.R
Make simulated data's names of columns consistent to analysis set. And change the test script accordingly.

@@ -77,6 +77,11 @@ for (date in Date_seq) {
   }
 }
 
+# Make names of columns consistent to other sets
+simulated_dataset <- simulated_dataset |>
+  janitor::clean_names()
+
+
 # View the first few rows of the simulated dataset
 # head(simulated_dataset)
 

### 2024-09-26 scripts/03-test_data.R

@@ -22,14 +22,14 @@ cat("Total missing values: ", num_missing_values, "\n")
 
 
 ## TEST2: Negative value (Total_Occupancy and Total_Capacity)
-negative_occupancy <- sum(simulated_dataset$Total_Occupancy < 0)
-negative_capacity <- sum(simulated_dataset$Total_Capacity < 0)
+negative_occupancy <- sum(simulated_dataset$total_occupancy < 0)
+negative_capacity <- sum(simulated_dataset$total_capacity < 0)
 cat("Total negative occupancy values: ", negative_occupancy, "\n")
 cat("Total negative capacity values: ", negative_capacity, "\n")
 
 
 ## TEST3: Date Format is consistent
-incorrect_dates <- sum(!grepl("^\\d{4}-\\d{2}-\\d{2}$", simulated_dataset$OCCUPANCY_DATE))
+incorrect_dates <- sum(!grepl("^\\d{4}-\\d{2}-\\d{2}$", simulated_dataset$date))
 
 if (incorrect_dates > 0) {
   message("Warning: ", incorrect_dates, " dates are not in the correct format (YYYY-MM-DD).")

### 2024-09-26 paper/paper.qmd
Write introduction and abstract, with relavant pakages, and relevant papers cited.

@@
   - Maggie Zhang
-thanks: "Code and data are available at:https://github.com/MaggieZ111119/marriage.git"
+thanks: "Code and data are available at:https://github.com/MaggieZ111119/CityofToronto_Daily_Shelter_Occupancy.Rproj.git"
 date: today
 date-format: long
-abstract: "This is an analysis study on marriage data set in from Toronto.
-The goal is to examine the impact of marriage on influencing the social and financial status of individuals.
-The result carrying out supporting roles for sustainability improvements, financial support, public policy forming, etc."
+abstract: "This paper investigates the occupancy of shelters in Toronto from 2017 to 2020, focusing on capacity and usage across different shelter sectors.
+By analyzing the data, we explore how shelter demand {exceeded available resources in certain sectors.
+This research highlights significant challenges faced by the shelter system, providing insights into the strain on resources and potential gaps in support for the homeless population}.
+These findings are crucial for informing policies and improving resource allocation to better address homelessness in Toronto."
 format: pdf
@@
 
+# Preparation
+
+#Load used libraries
 library(tidyverse)
 library(ggplot2)
+library(dplyr)
+library(knitr)
 
-# Read Data(Quarto need dataset to be readed in the file)
-data <- read_csv(here::here("data/analysis_data/cleaned_data.csv"))
+# Read Data(Quarto need data set to be readed in the file)
+shelter_data <- read_csv(here::here("~/CityofToronto_Daily_Shelter_Occupancy.Rproj/data/analysis_data/full_shelter_data.csv"))
 ```
@@
 
-The Data are extracted from @OpenDataToronto, learn and used @citeR and @rohan.
+Homelessness is a persistent and complex issue in many urban areas, and Toronto is no exception.
+As one of Canada’s largest cities, Toronto faces significant challenges in providing adequate shelter for its homeless population.The city operates a range of shelters that serve various groups, including men, women, youth, and families.
+The balance between availability and the demand for these services is crucial for both the well-being of individuals experiencing homelessness and the government's efforts to reduce homelessness population.
+Understanding how shelter occupancy changes over time, especially during critical periods, is essential for identifying gaps in resources and shaping effective policy responses.
+
+This paper focuses on analyzing shelter occupancy data from 2017 to 2020 in City of Toronto.
+The data which offers a detailed look at the city’s shelter during this time of period is provided on @OpenDataToronto portal.
+By examining trends in occupancy through the data, we aim to assess how well Toronto's shelters met the demand for space and where shortages may have occurred.
+By focusing on specific sectors of the shelter system, pinpoint which groups may have been disproportionately affected by resource limitations.
+
+FINDING!
+This study addresses a clear gap in the current literature by providing an up-to-date analysis of Toronto's shelter capacity and usage during a time of unprecedented public health and social challenges.
+___ NOTICE!!
+
+The remiander of this paper are in presented in sections: @sec-data Data, @sec-results Results, and @sec-discussion Discussion.
+The data section introduce the dataset used for analysis, expalinin its source and context that shaped its collection.This section thoroughly summarizes the data using visualizations created with ggplot2 (@R-ggplot2) and tables produced with knitr (@R-knitr).
+Key variables chosen for the analysis, along with the reasoning behind their selection, are explained.
+The results section presents the findings drawn from the data, highlighting patterns in shelter occupancy and compare to it's availability.
+Following by the discussion section, which explores the implications of these findings, particularly in relation to resource allocation and policy development, offering insights into how Toronto's shelter system responded to increasing demand.
 
 # Data {#sec-data}
+City that has record of offering shleter servise incluede: Toronto, North York, Scarborough, and Etobicoke.
 
-# Results
+# Results {#sec-results}
 This histogram (@fig-marriagedata) reflects the amount new marriage happens each year from the year of 2011 to 2024 according to @OpenDataToronto.
@@
 
-ggplot(data = data, 
-       aes(x = year, y = marriage_licenses)) +
-  geom_bar(stat = "identity") + labs(title = "Amount New Marriage Each Year 2011 - 2024", x = "Year", y = "Marriage Number")
 ```
 
-# Discussion
+# Discussion {#sec-discussion}
 

### 2024-09-26 paper/paper.qmd
more revise on abstract and introduction

@@
 # Read Data(Quarto need data set to be readed in the file)
-shelter_data <- read_csv(here::here("~/CityofToronto_Daily_Shelter_Occupancy.Rproj/data/analysis_data/full_shelter_data.csv"))
+shelter_data <- read_csv(here::here("~/CityofToronto_Daily_Shelter_Occupancy.Rproj/data/analysis_data/full_shelter_data.csv"), show_col_types = FALSE)
 ```
@@
 
-Homelessness is a persistent and complex issue in many urban areas, and Toronto is no exception.
-As one of Canada’s largest cities, Toronto faces significant challenges in providing adequate shelter for its homeless population.The city operates a range of shelters that serve various groups, including men, women, youth, and families.
+Homelessness is a persistent and complex issue in many areas in Canada(@gaetz2010struggle), and Toronto is no exception.
+As one of Canada’s largest cities, Toronto faces significant challenges in helping homeless people, who are unable to spend on housing largely due to poverty, to meet the necessities of living(@jadidzadeh2018patterns).
+The city operates a range of shelters that serve various groups, including men, women, youth, and families.
 The balance between availability and the demand for these services is crucial for both the well-being of individuals experiencing homelessness and the government's efforts to reduce homelessness population.
-Understanding how shelter occupancy changes over time, especially during critical periods, is essential for identifying gaps in resources and shaping effective policy responses.
+Understanding how shelter occupancy changes over time is essential for identifying gaps in resources and shaping effective policy responses.
 
@@
 
-The remiander of this paper are in presented in sections: @sec-data Data, @sec-results Results, and @sec-discussion Discussion.
+The remiander of this paper are in presented in sections: @sec-data : Data, @sec-results :Results, and @sec-discussion :Discussion.
 The data section introduce the dataset used for analysis, expalinin its source and context that shaped its collection.This section thoroughly summarizes the data using visualizations created with ggplot2 (@R-ggplot2) and tables produced with knitr (@R-knitr).
@@
 # Results {#sec-results}
-This histogram (@fig-marriagedata) reflects the amount new marriage happens each year from the year of 2011 to 2024 according to @OpenDataToronto.
-
-```{r}
-#| label: fig-marriagedata
-#| fig-cap: Marriage
-#| echo: false
-
-```
+This histogram reflects the amount new marriage happens each year from the year of 2011 to 2024 according to @OpenDataToronto.
 

### 2024-09-27 paper/paper.qmd
Complete data section, and with relavent paper cited to my paper

@@
 The remiander of this paper are in presented in sections: @sec-data : Data, @sec-results :Results, and @sec-discussion :Discussion.
-The data section introduce the dataset used for analysis, expalinin its source and context that shaped its collection.This section thoroughly summarizes the data using visualizations created with ggplot2 (@R-ggplot2) and tables produced with knitr (@R-knitr).
+The data section introduce the dataset used for analysis, expalinin its source and context that shaped its collection.This section thoroughly summarizes the data using visualizations created with `ggplot2` (@R-ggplot2) and tables produced with `knitr` (@R-knitr).
 Key variables chosen for the analysis, along with the reasoning behind their selection, are explained.
@@
 
+## Overview {#sec-data-overview}
+All data reviewed and analysis in this paper is the Daily Shelter Occupancy @Shelter.
+The data is essential for evaluating how shelters serve different populations (e.g., men, women, youth, families) and for analyzing the current shelter servise system over time, such as capacity shortfalls or surpluses.
+It provides inforamtion on all the active shelters exist in the City of Toronto area, collected in forms of four separate datasets corresponding to the years 2017, 2018, 2019, and 2020.
+Each datasets include various characteristics of the shelters.
+The data was sourced from an Open Data Toronto Portal @OpenDataToronto, with each row indicate a unique entry for a specific sector of specific shelter, on a specific date, and has Unique row identifier for Open Data database, "_id".
+
+The collection process records information about corresponding name of the non-profit entity that is responsible for the shelter, as well as the name of the facility (e.g.
+hotel, residence building), along with and their capacity to accommodate homeless clients.
+The Capacity is being measured as number of bed or a mat/cot available.
+Something will happen is that for the family sector, it is possible to exceed available capacity depending on the bed number, because family could be accommodated in a room with number beds smaller than number of people in their family.
+The data was collected every day, 4:00 AM, to record number of homeless clients occupying the shelters.
+This way to gather information about occupancy provides a consistent snapshot of shelter use across all organizations.
+
+Other similar datasets, especialy the ther dataset publish by Toronto Shelter & Support Services, were considered.
+However, they did not offer the cross-sector view of both occupancy and capacity needed for the focus of this analysis.
+The selected dataset allows for a broad comparison across time and sectors in different city, providing a fuller picture of trends within the shelter system.
+
+## Feature Selection and Aggregation
+
+For the purpose of this analysis, several features are chose to be particularly focused on.
+variable of interest including the the city (named "SHELTER_CITY" in the dataset) in which shelters are located; the date of data recorded("OCCUPANCY_DATE"); the sector("SECTOR") of clientele the shelters serve, for example men, women, youth, families, and even co-ed; the shelter's capacities("CAPACITY") and occupancy("OCCUPANCY") levels.
+These variables were chosen for their relevance in which is to investigate shelter occupancy and capacity across different cities and sectors, focusing on the City of Toronto from 2017 to 2020.
+
+There are also seven other detailed feature in the datasets: "ORGANIZATION_NAME", "SHELTER_NAME", "SHELTER_ADDRESS", "SHELTER_PROVINCE", "SHELTER_POSTAL_CODE", "FACILITY_NAME", and "PROGRAM_NAME".
+Using R programming lanaguage @citeR, the `janitor`@R-janitor, `tidyverse` @R-tidyverse, and `dplyr` @R-dplyr pakages are used in data simulation, downloading, cleaning, and writting test.
+No new variables were created for this analysis, but the data was aggregated by grouping observations by city, date, and sector.
+This aggregation facilitated a more comprehensive comparison across cities and sector groups.
+A random sample of the cleaned data can be seen in @sample-shelter.
+```{r}
+#| label: sample-shelter
+#| tbl-cap: Sample of Cleaned Shelter Data
+#| echo: false
+
+set.seed(1009633096)
+indices <- sample(1:nrow(shelter_data), 5)
+
+kable(shelter_data[indices,])
+
+```
+
+## Data Breakdown
+As shown in @shelter-full-table, The four cities being observed in the dataset are Toronto, Etobicoke, North York, and Scarborough.
+The sectors recorded include Co-ed (mixture), Families, Men, Women, and Youth.
+```{r}
+#| label: shelter-full-table
+#| tbl-cap: Number of Observations by City and Sector
+#| echo: false
+#| 
+# Count the number of observations by city and sector
+city_sector_breakdown <- shelter_data %>%
+  group_by(shelter_city, sector) %>%
+  count() %>%
+  spread(key = sector, value = n, fill = 0)
+
+# Check if the total is being calculated correctly
+city_sector_breakdown$Sum <- rowSums(city_sector_breakdown[,2:6], na.rm = TRUE)
+
+# Display the table with correct formatting
+city_sector_breakdown %>%
+  kable(caption = "Number of Observations by City and Sector, including all sectors")
+
+```
+
+The following table provides a summary of the average, maximum, and minimum occupancy, as well as capacity metrics for each city.
+```{r}
+#| label: shelter-by-city
+#| tbl-cap: Statistics for Homeless Shelter Occupancy by City
+#| echo: false
+
+# Because the data originally has one date and is separated into several rows with different sectors. 
+# If I want to calculate the total occupancy of that date in that city, I need to add all sector information together. Then, we will see the average, max, mix of occupancy. 
+# Same idea to capacity.
+
+toronto_data <- shelter_data %>% 
+  filter(shelter_city == "Toronto") %>% 
+  group_by(occupancy_date) %>%
+  summarise(
+    total_occupancy = sum(total_occupancy, na.rm = TRUE),
+    total_capacity = sum(total_capacity, na.rm = TRUE),
+    .groups = 'drop'
+  )
+
+north_york_data <- shelter_data %>% 
+  filter(shelter_city == "North York") %>%
+  group_by(occupancy_date) %>%
+  summarise(
+    total_occupancy = sum(total_occupancy, na.rm = TRUE),
+    total_capacity = sum(total_capacity, na.rm = TRUE),
+    .groups = 'drop'
+  )
+
+scarborough_data <- shelter_data %>% 
+  filter(shelter_city == "Scarborough")%>%
+  group_by(occupancy_date) %>%
+  summarise(
+    total_occupancy = sum(total_occupancy, na.rm = TRUE),
+    total_capacity = sum(total_capacity, na.rm = TRUE),
+    .groups = 'drop'
+  )
+
+etobicoke_data <- shelter_data %>% 
+  filter(shelter_city == "Etobicoke") %>%
+  group_by(occupancy_date) %>%
+  summarise(
+    total_occupancy = sum(total_occupancy, na.rm = TRUE),
+    total_capacity = sum(total_capacity, na.rm = TRUE),
+    .groups = 'drop'
+  )
+
+# Summary statistics for each city
+toronto_summary <- toronto_data %>%
+  summarise(
+    avg_occupancy = mean(total_occupancy, na.rm = TRUE),
+    max_occupancy = max(total_occupancy, na.rm = TRUE),
+    min_occupancy = min(total_occupancy, na.rm = TRUE),
+    avg_capacity = mean(total_capacity, na.rm = TRUE),
+    max_capacity = max(total_capacity, na.rm = TRUE),
+    min_capacity = min(total_capacity, na.rm = TRUE)
+  )
+
+north_york_summary <- north_york_data %>%
+  summarise(
+    avg_occupancy = mean(total_occupancy, na.rm = TRUE),
+    max_occupancy = max(total_occupancy, na.rm = TRUE),
+    min_occupancy = min(total_occupancy, na.rm = TRUE),
+    avg_capacity = mean(total_capacity, na.rm = TRUE),
+    max_capacity = max(total_capacity, na.rm = TRUE),
+    min_capacity = min(total_capacity, na.rm = TRUE)
+  )
+
+scarborough_summary <- scarborough_data %>%
+  summarise(
+    avg_occupancy = mean(total_occupancy, na.rm = TRUE),
+    max_occupancy = max(total_occupancy, na.rm = TRUE),
+    min_occupancy = min(total_occupancy, na.rm = TRUE),
+    avg_capacity = mean(total_capacity, na.rm = TRUE),
+    max_capacity = max(total_capacity, na.rm = TRUE),
+    min_capacity = min(total_capacity, na.rm = TRUE)
+  )
+
+etobicoke_summary <- etobicoke_data %>%
+  summarise(
+    avg_occupancy = mean(total_occupancy, na.rm = TRUE),
+    max_occupancy = max(total_occupancy, na.rm = TRUE),
+    min_occupancy = min(total_occupancy, na.rm = TRUE),
+    avg_capacity = mean(total_capacity, na.rm = TRUE),
+    max_capacity = max(total_capacity, na.rm = TRUE),
+    min_capacity = min(total_capacity, na.rm = TRUE)
+  )
+
+city <- c("Toronto", "North York", "Scarborough", "Etobicoke")
+combined_summary <- bind_rows(toronto_summary,
+                          north_york_summary,
+                          scarborough_summary,
+                          etobicoke_summary)
+combined_summary$city <- city
+combined_summary <- combined_summary %>%
+  select(city, everything())
+
+kable(combined_summary, 
+             col.names = c("City", 
+                           "Average Occupancy", 
+                           "Max Occupancy", 
+                           "Min Occupancy", 
+                           "Average Capacity", 
+                           "Max Capacity", 
+                           "Min Capacity"))
+```
+The relastion ship of two key feature, occupancy and capacity, are essential for understaidng current shelter servise system.
+The relashipship is reflected in @fig-occupancy-capacity-relashionship.
+More learning on the shelter servise and thier trend, and how they reflect the fomeless population are done, and will be discuss in the next section @sec-result.
+```{r}
+#| label: fig-occupancy-capacity-relashionship
+#| fig-cap: Relationship Between Total Occupancy and Total Capacity in Shelter of the City of Toronto
+#| fig-pos: "H"
+#| echo: false
+#| message: false
+
+ggplot(shelter_data, aes(x = total_capacity, y = total_occupancy, color = sector)) +
+  geom_point(alpha = 0.5) + 
+  geom_smooth(method = "lm", se = FALSE) +
+  labs(title = "Relationship Between Total Occupancy and Total Capacity in Toronto Shelters",
+       x = "Total Capacity",
+       y = "Total Occupancy",
+       color = "Sector") +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1")
+
+```
+
 # Results {#sec-results}
-This histogram reflects the amount new marriage happens each year from the year of 2011 to 2024 according to @OpenDataToronto.
+Through phafical study of the datset, some usful information are found and the result will be dicussed in this section. These will __________________________
+
+## Shelter Occupancy Trend over Time
+The figure
+```{r}
+#| label: shelter-over-time
+#| fig-cap: Visualization of Shelter _____ During Time Period 2017 to 2020
+#| echo: false
+#| message: false
+
+# Assuming you have a data frame 'shelter_data' with total occupancy for each city
+# Create individual plots for each city
+toronto_plot <- ggplot(toronto_data %>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+  geom_line(color = "blue") +
+  labs(title = "Toronto Occupancy Trends",
+       x = "Date",
+       y = "Total Occupancy") +
+  theme_minimal()
+
+north_york_plot <- ggplot(north_york_data%>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+  geom_line(color = "green") +
+  labs(title = "North York Occupancy Trends",
+       x = "Date",
+       y = "Total Occupancy") +
+  theme_minimal()
+
+scarborough_plot <- ggplot(scarborough_data%>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+  geom_line(color = "red") +
+  labs(title = "Scarborough Occupancy Trends",
+       x = "Date",
+       y = "Total Occupancy") +
+  theme_minimal()
+
+etobicoke_plot <- ggplot(etobicoke_data%>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+  geom_line(color = "orange") +
+  labs(title = "Etobicoke Occupancy Trends",
+       x = "Date",
+       y = "Total Occupancy") +
+  theme_minimal()
+
+# Present 4 plot together
+combined_plots <- grid.arrange(toronto_plot, north_york_plot,
+                                scarborough_plot, etobicoke_plot,
+                                nrow = 2, ncol = 2)
+
+combined_plots
+
+```
+
+## Shelter Ustillization Analysis
+To analyze capacity utilization for the four cities—Toronto, North York, Scarborough, and Etobicoke— calculate the capacity utilization rate for each city over time and visualize this data. 
+```{r}
+#| label: shelter-utilization
+#| fig-cap: Change in Utilization Rate Average on All Shelters by City (2017-2020)
+#| echo: false
+#| message: false
+
+# Calculate utilization rate by city
+toronto_data <- toronto_data %>%
+  mutate(utilization_rate = total_occupancy / total_capacity)
+
+north_york_data <- north_york_data %>%
+  mutate(utilization_rate = total_occupancy / total_capacity)
+
+scarborough_data <- scarborough_data %>%
+  mutate(utilization_rate = total_occupancy / total_capacity)
+
+etobicoke_data <- etobicoke_data %>%
+  mutate(utilization_rate = total_occupancy / total_capacity)
+
+# Combine all city datasets
+combined_data <- bind_rows(
+  toronto_data %>% mutate(shelter_city = "Toronto"),
+  north_york_data %>% mutate(shelter_city = "North York"),
+  scarborough_data %>% mutate(shelter_city = "Scarborough"),
+  etobicoke_data %>% mutate(shelter_city = "Etobicoke")
+)
+
+# Extract year from occupancy_date
+combined_data <- combined_data %>%
+  mutate(year = year(occupancy_date))
+
+# Calculate average utilization rate by year and city
+annual_utilization <- combined_data %>%
+  group_by(year, shelter_city) %>%
+  summarise(avg_utilization_rate = mean(utilization_rate, na.rm = TRUE), .groups = 'drop')
+
+ggplot(annual_utilization, aes(x = year, y = avg_utilization_rate, color = shelter_city)) +
+  geom_line(size = 1) +
+  geom_point(size = 2) +
+  labs(x = "Year",
+       y = "Average Utilization Rate",
+       color = "City") +
+  theme_minimal() +
+  scale_y_continuous(labels = scales::percent_format(scale = 100))  
+```
+
+## Over Capacity Cases
+Back to the original dataset, identify cases where shelter capacity is exceeded (i.e., occupancy > capacity) and understand the frequency and distribution of these events.
+```{r}
+#| label: over-capacity
+#| tbl-cap: Overcrowded Cases by City and Sector
+#| echo: false
+#| message: false
+
+# Filter for overcrowded data
+overcrowded_data <- shelter_data %>%
+  filter(total_occupancy > total_capacity)
+
+# Create a frequency table including all cities and sectors
+frequency_table <- overcrowded_data %>%
+  group_by(shelter_city, sector) %>%
+  summarise(count = n(), .groups = 'drop') %>%
+  complete(shelter_city, sector, fill = list(count = 0)) %>%
+  pivot_wider(names_from = sector, values_from = count)
+
+# Create a complete dataset of all combinations of cities and sectors
+all_combinations <- expand.grid(
+  shelter_city = unique(shelter_data$shelter_city),
+  sector = unique(shelter_data$sector)
+)
+
+# Create a frequency table including all cities and sectors
+frequency_table <- overcrowded_data %>%
+  group_by(shelter_city, sector) %>%
+  summarise(count = n(), .groups = 'drop') %>%
+  right_join(all_combinations, by = c("shelter_city", "sector")) %>%
+  replace_na(list(count = 0)) %>%
+  pivot_wider(names_from = sector, values_from = count, values_fill = 0)
+
+# View the frequency table with knitr
+frequency_table %>%
+  kable()
+
+```
+
+s
 

### 2024-09-27 scripts/02-data_cleaning.R

@@ -35,12 +35,12 @@ cleaned_2017 <- cleaned_2017 |>
   group_by(occupancy_date,shelter_city,sector) |> 
   summarize(
     # occupancy number in each city for each sector 
-    totoal_occupancy = sum(occupancy, na.rm = TRUE),
+    total_occupancy = sum(occupancy, na.rm = TRUE),
     # occupancy number in each city for each sector 
-    totoal_capacity = sum(capacity, na.rm = TRUE),
+    total_capacity = sum(capacity, na.rm = TRUE),
     .groups = 'drop') |>
   select(occupancy_date, shelter_city, sector, 
-         totoal_occupancy, totoal_capacity)
+         total_occupancy, total_capacity)
 
 # Make sure date format is consistent with other three datasets
 cleaned_2017$occupancy_date <-  as.Date(cleaned_2017$occupancy_date, 
@@ -59,12 +59,12 @@ cleaned_2018 <- cleaned_2018 |>
   group_by(occupancy_date,shelter_city,sector) |> 
   summarize(
     # occupancy number in each city for each sector 
-    totoal_occupancy = sum(occupancy, na.rm = TRUE),
+    total_occupancy = sum(occupancy, na.rm = TRUE),
     # occupancy number in each city for each sector 
-    totoal_capacity = sum(capacity, na.rm = TRUE),
+    total_capacity = sum(capacity, na.rm = TRUE),
     .groups = 'drop') |>
   select(occupancy_date, shelter_city, sector, 
-         totoal_occupancy, totoal_capacity)
+         total_occupancy, total_capacity)
 
 # Make sure date format is consistent with other three datasets
 cleaned_2018$occupancy_date <-  as.Date(cleaned_2018$occupancy_date, 
@@ -82,12 +82,12 @@ cleaned_2019 <- cleaned_2019 |>
   group_by(occupancy_date,shelter_city,sector) |> 
   summarize(
     # occupancy number in each city for each sector 
-    totoal_occupancy = sum(occupancy, na.rm = TRUE),
+    total_occupancy = sum(occupancy, na.rm = TRUE),
     # occupancy number in each city for each sector 
-    totoal_capacity = sum(capacity, na.rm = TRUE),
+    total_capacity = sum(capacity, na.rm = TRUE),
     .groups = 'drop') |>
   select(occupancy_date, shelter_city, sector, 
-         totoal_occupancy, totoal_capacity)
+         total_occupancy, total_capacity)
 
[…]

### 2024-09-27 paper/paper.qmd
change some reference errors
Correct cross-references

@@
 library(knitr)
+library(gridExtra)
 
@@
 This aggregation facilitated a more comprehensive comparison across cities and sector groups.
-A random sample of the cleaned data can be seen in @sample-shelter.
+A random sample of the cleaned data can be seen in @fig-sample-shelter.
 ```{r}
-#| label: sample-shelter
+#| label: fig-sample-shelter
 #| tbl-cap: Sample of Cleaned Shelter Data
@@
 ## Data Breakdown
-As shown in @shelter-full-table, The four cities being observed in the dataset are Toronto, Etobicoke, North York, and Scarborough.
+As shown in @fig-shelter-full-table, The four cities being observed in the dataset are Toronto, Etobicoke, North York, and Scarborough.
 The sectors recorded include Co-ed (mixture), Families, Men, Women, and Youth.
 ```{r}
-#| label: shelter-full-table
+#| label: fig-shelter-full-table
 #| tbl-cap: Number of Observations by City and Sector
@@
 
-The following table provides a summary of the average, maximum, and minimum occupancy, as well as capacity metrics for each city.
+The following table @fig-shelter-by-city provides a summary of the average, maximum, and minimum occupancy, as well as capacity metrics for each city.
 ```{r}
-#| label: shelter-by-city
+#| label: fig-shelter-by-city
 #| tbl-cap: Statistics for Homeless Shelter Occupancy by City
@@
 The relashipship is reflected in @fig-occupancy-capacity-relashionship.
-More learning on the shelter servise and thier trend, and how they reflect the fomeless population are done, and will be discuss in the next section @sec-result.
+More learning on the shelter servise and thier trend, and how they reflect the fomeless population are done, and will be discuss in the next section @sec-results
 ```{r}
@@
 
-s
-
 # Discussion {#sec-discussion}

### 2024-09-27 paper/paper.qmd
Cross references changed

@@
 This aggregation facilitated a more comprehensive comparison across cities and sector groups.
-A random sample of the cleaned data can be seen in @fig-sample-shelter.
+A random sample of the cleaned data can be seen in @fig-shelter-sample.
 ```{r}
-#| label: fig-sample-shelter
+#| label: fig-shelter-sample
 #| tbl-cap: Sample of Cleaned Shelter Data
 #| echo: false
+#| message: false
 
@@
 
-kable(shelter_data[indices,])
+kable(shelter_data[indices,],
+      caption = "Sample of Cleaned Shelter Data")
 
@@
 #| echo: false
-#| 
+#| message: false
+
 # Count the number of observations by city and sector
@@
 city_sector_breakdown %>%
-  kable(caption = "Number of Observations by City and Sector, including all sectors")
+  kable(caption = "Number of Observations by City and Sector")
 
@@
 
-The following table @fig-shelter-by-city provides a summary of the average, maximum, and minimum occupancy, as well as capacity metrics for each city.
+The following table @fig-shelter-diff-city provides a summary of the average, maximum, and minimum occupancy, as well as capacity metrics for each city.
 ```{r}
-#| label: fig-shelter-by-city
+#| label: fig-shelter-diff-city
 #| tbl-cap: Statistics for Homeless Shelter Occupancy by City
 #| echo: false
+#| message: false
 
@@
                            "Max Capacity", 
-                           "Min Capacity"))
+                           "Min Capacity"),
+      caption = "Statistics for Homeless Shelter Occupancy by City")
 ```
@@
   geom_smooth(method = "lm", se = FALSE) +
-  labs(title = "Relationship Between Total Occupancy and Total Capacity in Toronto Shelters",
+  labs(title = "Relationship Between Total Occupancy and Total Capacity in Shelter of the City of Toronto",
        x = "Total Capacity",
@@
 ## Shelter Occupancy Trend over Time
-The figure
+The figure @fig-shelter-over-time, a
 ```{r}
-#| label: shelter-over-time
-#| fig-cap: Visualization of Shelter _____ During Time Period 2017 to 2020
+#| label: fig-shelter-over-time
+#| fig-cap: Visualization of Shelter Occupancy During Time Period 2017 to 2020
 #| echo: false
@@
 
-# Present 4 plot together
-combined_plots <- grid.arrange(toronto_plot, north_york_plot,
+combined_plot <- grid.arrange(toronto_plot, north_york_plot, 
                                scarborough_plot, etobicoke_plot, 
-                                nrow = 2, ncol = 2)
+                               nrow = 2, ncol = 2,
+                               top = "Visualization of Shelter Occupancy During Time Period 2017 to 2020"
+                          )
 
-combined_plots
+# This will suppress the grid output in the document
+invisible(combined_plot)
 
@@
 To analyze capacity utilization for the four cities—Toronto, North York, Scarborough, and Etobicoke— calculate the capacity utilization rate for each city over time and visualize this data.
+See @fig-shelter-utilization.
 ```{r}
-#| label: shelter-utilization
+#| label: fig-shelter-utilization
 #| fig-cap: Change in Utilization Rate Average on All Shelters by City (2017-2020)
@@
 #| message: false
+#| warning: false
 
@@
        y = "Average Utilization Rate",
-       color = "City") +
+       color = "City",
+       caption = "Utilization Rate Average Change on All Shelters by City") +
   theme_minimal() +
@@
 ## Over Capacity Cases
-Back to the original dataset, identify cases where shelter capacity is exceeded (i.e., occupancy > capacity) and understand the frequency and distribution of these events.
+Back to the original dataset, identify cases where shelter capacity is exceeded (i.e., occupancy > capacity) and understand the frequency and distribution of these events. see @fig-overcapacity, under
 ```{r}
-#| label: over-capacity
+#| label: fig-overcapacity
 #| tbl-cap: Overcrowded Cases by City and Sector
@@
 frequency_table %>%
-  kable()
+  kable(caption = "Overcrowded Cases by City and Sector")
 

### 2024-09-27 paper/paper.qmd
Result part finished

@@
 # Data {#sec-data}
-City that has record of offering shleter servise incluede: Toronto, North York, Scarborough, and Etobicoke.
-
-## Overview {#sec-data-overview}
 All data reviewed and analysis in this paper is the Daily Shelter Occupancy @Shelter.
@@
 It provides inforamtion on all the active shelters exist in the City of Toronto area, collected in forms of four separate datasets corresponding to the years 2017, 2018, 2019, and 2020.
+
+## Overview {#sec-data-overview}
 Each datasets include various characteristics of the shelters.
@@
 The sectors recorded include Co-ed (mixture), Families, Men, Women, and Youth.
+Across all cities, record for Youth age group being presents.
+In fact, Youth is the only population in Etobicoke and North York.
+In Toronto, which has the most number of observation recorded, equal number of sectors are being observed, but how these people in distributed inthe total popluation are not clear.
+This will be further addressed in the following sections.
 ```{r}
@@
 The following table @fig-shelter-diff-city provides a summary of the average, maximum, and minimum occupancy, as well as capacity metrics for each city.
+Toronto has most amount of shelter avaliable and also has most people occuupaying in.
+The Maximum occupany of Toronto in a day, combined all sectors, from 2017 to 2020,is 6803.
+Wheras Etobicoke only has 53 people occupanying.
+The fact that Etotobike has only hoemless people in the group of Youth recorded could explain alittle bit.
+But, the de=ifference still strong enough to see that the homeless population might be significant larger in Toronto compared to aother cities.
 ```{r}
@@
 The relashipship is reflected in @fig-occupancy-capacity-relashionship.
-More learning on the shelter servise and thier trend, and how they reflect the fomeless population are done, and will be discuss in the next section @sec-results
+Occupany and capacity are greatly follwing a positive correlation, indicating that most there aren't much over-investment to the shelter system, nor heavily over-filled shelter.
+But there are noticible deviation from the perfect correlation to above, these are suggecting there are cases where occupany is higher than capacity, suggesting occupantee may living in a overly paked places.
+More will be dicussed in  @sec-results, including other learning on the shelter servise like thier trend, and how these shelter information possiblly reflect the homeless.
 ```{r}
@@
 # Results {#sec-results}
-Through phafical study of the datset, some usful information are found and the result will be dicussed in this section. These will __________________________
+Through grpahfical study of the datset, some usful information are found and the result will be dicussed in this section.
 
 ## Shelter Occupancy Trend over Time
-The figure @fig-shelter-over-time, a
+The figure @fig-shelter-over-time as dipict the trend of homless poeple occupiying shelters in each city.
+A high in occupancy are notice in all four city around the time between late 2019 to early 2020.
+Especially, there is a obviouse rising trend in Scarborough.
+Combined with the information on the "About Daily Shelter Occupancy" section in the data website @Shelter, it rise may be subjectted to the ourbreak of COVID_19.
+The occpany number going significantly decrease from mid 2020, across all four cities also suggest this finding.
 ```{r}
@@
 
-## Shelter Ustillization Analysis
-To analyze capacity utilization for the four cities—Toronto, North York, Scarborough, and Etobicoke— calculate the capacity utilization rate for each city over time and visualize this data.
-See @fig-shelter-utilization.
+## Shelter Utilization Analysis
+The Utilization Rate as being calculated as:
+$$\text{Utilization Rate} = \left( \frac{\text{Number of Occupancy}}{\text{Number of Capacity}} \right) \times 100\%$$
+From @fig-shelter-utilization, it's the utilization rate in Toronto remains the lowest over 4 years almost all the time compared to other cities, but still in a relativly high number.
+This suggest that shelter servise croass all four cities are not over-inveseting, their servise are actually helping the hoemelss population since alot of people are using them.
+There is a significant decrease in utilization rate from Fall 2019 to Summer 2020, despite the increase in occupation number as sugessted in @fig-shelter-over-time.
+This incicated that more shelter are timely provided, the goverment are providing larger amount of shelter than usual during pandemic.
+This actully can be visulized in @fig-shelter-provided, espcially in the case for Scarborugh, there is a noticibke peak at very end of 2019 and start of 2020.
 ```{r}
 #| label: fig-shelter-utilization
-#| fig-cap: Change in Utilization Rate Average on All Shelters by City (2017-2020)
+#| fig-cap: Yearly change in Utilization Rate Average on All Shelters by City (2017-2020)
 #| echo: false
@@
 combined_data <- combined_data %>%
-  mutate(year = year(occupancy_date))
+  mutate(year = year(occupancy_date),
+         month = month(occupancy_date),
+         season = case_when(
+           month %in% c(12, 1, 2) ~ "Winter",
+           month %in% c(3, 4, 5) ~ "Spring",
+           month %in% c(6, 7, 8) ~ "Summer",
+           month %in% c(9, 10, 11) ~ "Fall"
+         ))
 
-# Calculate average utilization rate by year and city
+# Have data into seasons
+combined_data <- combined_data %>%
+  mutate(season_year = factor(paste(season, year), 
+                               levels = c("Winter 2017", "Spring 2017", "Summer 2017", "Fall 2017",
+                                          "Winter 2018", "Spring 2018", "Summer 2018", "Fall 2018",
+                                          "Winter 2019", "Spring 2019", "Summer 2019", "Fall 2019",
+                                          "Winter 2020", "Spring 2020", "Summer 2020", "Fall 2020")))
+
+# Calculate average utilization rate
 annual_utilization <- combined_data %>%
-  group_by(year, shelter_city) %>%
+  group_by(season_year, shelter_city) %>%
   summarise(avg_utilization_rate = mean(utilization_rate, na.rm = TRUE), .groups = 'drop')
 
-ggplot(annual_utilization, aes(x = year, y = avg_utilization_rate, color = shelter_city)) +
+ggplot(annual_utilization, aes(x = season_year, y = avg_utilization_rate, color = shelter_city, group = shelter_city)) +
   geom_line(size = 1) +
   geom_point(size = 2) +
-  labs(x = "Year",
+  labs(x = "Seasons",
        y = "Average Utilization Rate",
@@
   theme_minimal() +
-  scale_y_continuous(labels = scales::percent_format(scale = 100))  
+  scale_y_continuous(labels = scales::percent_format(scale = 100)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+```{r}
+#| label: fig-shelter-provided
+#| fig-cap: Shelter Capacity During Time Period 2017 to 2020 of CIties
+#| echo: false
+#| message: false
+#| warning: false
+
+# Create individual plots for each city
+toronto_plot <- ggplot(
+  toronto_data %>% slice(seq(1, n(), by = 100)), 
+                         aes(x = occupancy_date, y = total_capacity)) +
+  geom_line(size = 1, color = "blue") +
+  geom_point(size = 2) +
+  labs(title = "Toronto", x = "Year", y = "Capacity") +
+  theme_minimal()
+
+north_york_plot <- ggplot(
+  north_york_data %>% slice(seq(1, n(), by = 100)), 
+  aes(x = occupancy_date, y = total_capacity)) +
+  geom_line(size = 1, color = "green") +
+  geom_point(size = 2) +
+  labs(title = "North York", x = "Year", y = "Capacity") +
+  theme_minimal()
+
+scarborough_plot <- ggplot(
+  scarborough_data %>% slice(seq(1, n(), by = 100)), 
+  aes(x = occupancy_date, y = total_capacity)) +
+  geom_line(size = 1, color = "red") +
+  geom_point(size = 2) +
+  labs(title = "Scarborough", x = "Year", y = "Capacity") +
+  theme_minimal()
+
+etobicoke_plot <- ggplot(
+  etobicoke_data %>% slice(seq(1, n(), by = 100)), 
+  aes(x = occupancy_date, y = total_capacity)) +
+  geom_line(size = 1, color = "orange") +
+  geom_point(size = 2) +
+  labs(title = "Etobicoke", x = "Year", y = "Capacity") +
+  theme_minimal()
+
+# Combine the four plots into a single figure
+combined_plot_cap <- grid.arrange(toronto_plot, north_york_plot, 
+                              scarborough_plot, etobicoke_plot, 
+                              nrow = 2, ncol = 2,
+                              top = "Visualization of Shelter Capacity During Time Period 2017 to 2020")
+
+# Display the combined plot
+invisible(combined_plot_cap)
+
 ```
@@
 ## Over Capacity Cases
-Back to the original dataset, identify cases where shelter capacity is exceeded (i.e., occupancy > capacity) and understand the frequency and distribution of these events. see @fig-overcapacity, under
+The relashipship between Occupancy and Capcity over this four year (see @fig-occupancy-capacity-relashionship) are revealling cases where more tha expectted people are living in the shelter, as we dicusssued in Data section @sec-data.
+These cases where capacity is exceeded (when $occupancy > capacity$) are importent when considering improvement shelter system improvement.
+By further invisted to the dataset, we are ablt to identify cases are actually happens to Families sector in Toronto (see @fig-overcapacity).
+And all other sector didn't expereince overcorwaaed shelter.
+Think incidate the quility of shleter servise is good at most case.
+Families sector are expereiceing overcraodded shelter does not implies the shelter system's fault, it is likely that families with children are assigned to a room with bed/mat that is smaller compared to thier family size.
+2 children are able to sleep in one bed, this does not seems like a proalem.
+For example, a family of five with small children, can elect to be accommodated in a room with four beds, as stated in explanamtion of "CAPACITY" feature in the Portal @Shelter.
+
 ```{r}
@@
 
-## First discussion point {#sec-first-point}
+## Shelter servise evaluation
 
-from the study, the Marriage number across Toronto is .....
+Based on the information said in @sec-results, particularly  @fig-shelter-utilization, we can see the selter servise system in the CIty of Toronto are indded good structured.
+The untillization rate is usually in the 90% - 100% region.
+Suggesting that what being provided are well-used and supportivie to the homeless community.
 
-## Second discussion point
+## COVID-19 Effect
 
-[My second point]
+Thorugh looking at the plot @fig-shelter-over-time, the ococupanny of shleters are at the highest around WInter 2019 to the begining of 2020.
+The pendenmic is indeed infecting the homeless population across four cities.
+Government actual in react to the outbreak of COVID-19, in intend to support homeless population are represnted on @fig-shelter-provided, with higher capacities of living nessecities provided.
+Thorugh higher capaciticies of existing shelter,s or adding in new shelters.
 
-## Third discussion point
-[My third point]
+## Weaknesses and next steps {#sec-weakness}
 
-## Weaknesses and next steps
-
-The study is not finalized, more detailed and careful data examination is needed.
+COVID-19 is inded empacting on homeless populations,
 

### 2024-09-27 paper/paper.qmd
write weakness and revise typos

@@
 
-Homelessness is a persistent and complex issue in many areas in Canada(@gaetz2010struggle), and Toronto is no exception.
-As one of Canada’s largest cities, Toronto faces significant challenges in helping homeless people, who are unable to spend on housing largely due to poverty, to meet the necessities of living(@jadidzadeh2018patterns).
-The city operates a range of shelters that serve various groups, including men, women, youth, and families.
-The balance between availability and the demand for these services is crucial for both the well-being of individuals experiencing homelessness and the government's efforts to reduce homelessness population.
-Understanding how shelter occupancy changes over time is essential for identifying gaps in resources and shaping effective policy responses.
+Homelessness remains a persistent issue across Canada, including in Toronto(@gaetz2010struggle).
+s one of the country’s largest cities, Toronto faces ongoing challenges in assisting individuals who, primarily due to poverty, cannot afford housing and struggle to meet basic needs(@jadidzadeh2018patterns).
+The City of Toronto operates a network of shelters catering to men, women, youth, and families, making it essential to balance the availability of these services with demand.
+Monitoring shelter occupancy trends with capacity is crucial for identifying resource gaps and developing effective policies to address the needs of homeless populations.
 
-This paper focuses on analyzing shelter occupancy data from 2017 to 2020 in City of Toronto.
-The data which offers a detailed look at the city’s shelter during this time of period is provided on @OpenDataToronto portal.
-By examining trends in occupancy through the data, we aim to assess how well Toronto's shelters met the demand for space and where shortages may have occurred.
-By focusing on specific sectors of the shelter system, pinpoint which groups may have been disproportionately affected by resource limitations.
+This paper analyzes shelter occupancy data from 2017 to 2020 in the City of Toronto, sourced from the Open Data Toronto portal (@OepnDataToronto).
+By examining occupancy trends during this period, particularly during the COVID-19 pandemic, we aim to evaluate how effectively the city's shelters met the increased demand.
+Our focus on specific sectors within the shelter system will help determine which groups were disproportionately affected and shed light on the system's adaptability in response to the crisis, particularly in addressing issues of overcrowding in family shelters.
 
-FINDING!
-This study addresses a clear gap in the current literature by providing an up-to-date analysis of Toronto's shelter capacity and usage during a time of unprecedented public health and social challenges.
-___ NOTICE!!
+By studying the shelter occupancy data from 2017 to 2020 across four cities, key findings emerged.
+There was an increase in shelter occupancy from late 2019 to early 2020, which coincided with the onset of the COVID-19 pandemic, particularly in Scarborough, which was observed to have higher than usual capacities of sheltering service during that period.
+Despite the rise in shelter use, the utilization rates remained high, indicating that the shelters were effectively meeting demand without being overburdened.
+The government's timely increase in shelter capacity during the pandemic was especially evident.
+Over Capacity sheltering experience exists, in Toronto's shelters for families, but it likely resulted from flexible accommodation arrangements rather than systemic flaws.
+Overall, the shelter system demonstrated well adaptability and support for homeless populations during this period.
 
-The remiander of this paper are in presented in sections: @sec-data : Data, @sec-results :Results, and @sec-discussion :Discussion.
-The data section introduce the dataset used for analysis, expalinin its source and context that shaped its collection.This section thoroughly summarizes the data using visualizations created with `ggplot2` (@R-ggplot2) and tables produced with `knitr` (@R-knitr).
+The remainder of this paper is presented in sections: @sec-data :Data, @sec-results :Results, @sec-discussion :Discussion, and @sec-weakness :Weaknesses and Next Steps.
+The data section introduces the dataset used for analysis, explaining its source and the context that shaped its collection.
+This section thoroughly summarizes the data using visualizations created with `ggplot2` (@R-ggplot2) and tables produced with `knitr` (@R-knitr), also with `gridExtra` (@gridExtra) to help formatting.
 Key variables chosen for the analysis, along with the reasoning behind their selection, are explained.
-The results section presents the findings drawn from the data, highlighting patterns in shelter occupancy and compare to it's availability.
-Following by the discussion section, which explores the implications of these findings, particularly in relation to resource allocation and policy development, offering insights into how Toronto's shelter system responded to increasing demand.
+The results section presents the findings drawn from the data, highlighting patterns in shelter occupancy and compare to its availability.
+Followed by the discussion section, which explores the implications of these findings, particularly in relation to resource allocation and policy development, offering insights into how Toronto's shelter system responded to increasing demand.
 
@@
 ## Shelter Occupancy Trend over Time
-The figure @fig-shelter-over-time as dipict the trend of homless poeple occupiying shelters in each city.
-A high in occupancy are notice in all four city around the time between late 2019 to early 2020.
-Especially, there is a obviouse rising trend in Scarborough.
-Combined with the information on the "About Daily Shelter Occupancy" section in the data website @Shelter, it rise may be subjectted to the ourbreak of COVID_19.
-The occpany number going significantly decrease from mid 2020, across all four cities also suggest this finding.
+The figure @fig-shelter-over-time depicts the trend of homeless people occupying shelters in each city over time.
+A noticeable peak in occupancy is observed across all four cities between late 2019 and early 2020.
+Especially, there is an rising trend in Scarborough.
+This rise coincides with the outbreak of COVID-19, as noted in the "About Daily Shelter Occupancy" section in the data website @ShelterThe.
+significant decrease in occupancy from mid-2020 across all cities further supports this correlation, suggesting the pandemic had a direct impact on shelter use.
 ```{r}
@@
 
-COVID-19 is inded empacting on homeless populations,
-
-\newpage
-
-\appendix
-
-# Appendix {-}
+COVID-19 is inded empacting on homeless populations, and the effor of mainting thier living needs is a continuse effort even 5 years after the outbreak.
+This data contains evidence for govemetn support during the pendemic, but is not inclusive enought to evluated on their performance on shelter servises.
+This defeinlty reqire more rigours research.
+And it's also not enought to say about what is the govement' support now, since this data only untill 2020.
+ALso, the increase untillization rate during covid outbreak could be the case that more people are facing more severe peoeblems so that not even make it to the shelter.
+Understanidng the well-velopneness and imparotance of support networks among people experiencing homelessness is sessential.
+A more cirtical proalblem comes along it how should the supporte being delievered.
+A good way to to support while ensuring not to disrupt them, for instance by avoiding practices that displace or isolate people from their communities such as moving people to shelters located far from their usual supports @boucher2022they.
+This is defienlt a long journey to go.
 

### 2024-09-27 paper/paper.qmd
More edits on discussion

@@
 $$\text{Utilization Rate} = \left( \frac{\text{Number of Occupancy}}{\text{Number of Capacity}} \right) \times 100\%$$
-From @fig-shelter-utilization, it's the utilization rate in Toronto remains the lowest over 4 years almost all the time compared to other cities, but still in a relativly high number.
-This suggest that shelter servise croass all four cities are not over-inveseting, their servise are actually helping the hoemelss population since alot of people are using them.
-There is a significant decrease in utilization rate from Fall 2019 to Summer 2020, despite the increase in occupation number as sugessted in @fig-shelter-over-time.
+As shown in @fig-shelter-utilization, Toronto almost consistently has the lowest utilization rate compared to the other cities over four years, although the rates remain relatively high.
+This suggests that shelter services are well-used and not over-invested, meaning that the shelters are indeed serving the homeless population effectively.
+Despite an increase in occupancy around the end of 2019, utilization rates decreased during this period, likely due to an increase in available shelter spaces provided during the COVID-19 pandemic, suggested in @fig-shelter-over-time.
 This incicated that more shelter are timely provided, the goverment are providing larger amount of shelter than usual during pandemic.
-This actully can be visulized in @fig-shelter-provided, espcially in the case for Scarborugh, there is a noticibke peak at very end of 2019 and start of 2020.
+This is particularly evident in Scarborough, where a sharp increase in shelter capacity is visible at the end of 2019 and the start of 2020.
+Refers to @fig-shelter-provided to observe more capacity changes in shelters over time.
 ```{r}
@@
 ## Over Capacity Cases
-The relashipship between Occupancy and Capcity over this four year (see @fig-occupancy-capacity-relashionship) are revealling cases where more tha expectted people are living in the shelter, as we dicusssued in Data section @sec-data.
-These cases where capacity is exceeded (when $occupancy > capacity$) are importent when considering improvement shelter system improvement.
-By further invisted to the dataset, we are ablt to identify cases are actually happens to Families sector in Toronto (see @fig-overcapacity).
-And all other sector didn't expereince overcorwaaed shelter.
-Think incidate the quility of shleter servise is good at most case.
-Families sector are expereiceing overcraodded shelter does not implies the shelter system's fault, it is likely that families with children are assigned to a room with bed/mat that is smaller compared to thier family size.
-2 children are able to sleep in one bed, this does not seems like a proalem.
-For example, a family of five with small children, can elect to be accommodated in a room with four beds, as stated in explanamtion of "CAPACITY" feature in the Portal @Shelter.
+The relationship between occupancy and capacity over the four years (@fig-occupancy-capacity-relashionship) reveals instances where shelter capacity was exceeded, as we discussed in the Data section (@sec-data).
+These cases where capacity is exceeded (when $occupancy > capacity$) are important to study when considering improvement shelter system improvement.
+By further investigation of the data, these overcrowded cases are primarily observed in the Families sector in Toronto (see @fig-overcapacity).
+Other sectors did not experience overcapacity, indicating that the shelter services were generally adequate.
+The possible overcrowding experience that happens to the Families sector may not necessarily reflect poor shelter conditions, as it could result from families being assigned to rooms with slightly fewer beds than their family size would suggest.
+For example, children might share beds (@Shelter), which does not indicate a systemic issue in shelter management.
 
@@
 
-Based on the information said in @sec-results, particularly  @fig-shelter-utilization, we can see the selter servise system in the CIty of Toronto are indded good structured.
-The untillization rate is usually in the 90% - 100% region.
-Suggesting that what being provided are well-used and supportivie to the homeless community.
+Based on the findings, particularly from the utilization rate data @fig-shelter-utilization, the shelter service system in the City of Toronto appears to be well-structured.
+Utilization rates consistently fall within the 90%-100% range, indicating that shelters are effectively supporting the homeless population.
 
-## COVID-19 Effect
+## COVID-19 Impact
 
-Thorugh looking at the plot @fig-shelter-over-time, the ococupanny of shleters are at the highest around WInter 2019 to the begining of 2020.
-The pendenmic is indeed infecting the homeless population across four cities.
-Government actual in react to the outbreak of COVID-19, in intend to support homeless population are represnted on @fig-shelter-provided, with higher capacities of living nessecities provided.
-Thorugh higher capaciticies of existing shelter,s or adding in new shelters.
+The occupancy of shelters reached its peak around winter 2019 to early 2020, as seen in @fig-shelter-over-time.
+This increase is likely linked to the COVID-19 pandemic, as shelters saw heightened demand.
+After this peak, occupancy dropped significantly.
+Suggesting the efforts by local governments to provide additional resources during the pandemic.
+The government intention to support homeless population is presented by higher capacities of living resources provided (see @fig-shelter-provided).
+These might be through higher capacities of existing shelters or adding in new shelters.
 
@@
 
-COVID-19 is inded empacting on homeless populations, and the effor of mainting thier living needs is a continuse effort even 5 years after the outbreak.
-This data contains evidence for govemetn support during the pendemic, but is not inclusive enought to evluated on their performance on shelter servises.
-This defeinlty reqire more rigours research.
-And it's also not enought to say about what is the govement' support now, since this data only untill 2020.
-ALso, the increase untillization rate during covid outbreak could be the case that more people are facing more severe peoeblems so that not even make it to the shelter.
-Understanidng the well-velopneness and imparotance of support networks among people experiencing homelessness is sessential.
-A more cirtical proalblem comes along it how should the supporte being delievered.
-A good way to to support while ensuring not to disrupt them, for instance by avoiding practices that displace or isolate people from their communities such as moving people to shelters located far from their usual supports @boucher2022they.
-This is defienlt a long journey to go.
+COVID-19 has significantly impacted homeless populations, and the effort to meet their needs continues even five years after the outbreak.
+This data provides evidence of government support during the pandemic, but it is not enough to evaluate the effectiveness of shelter services and other government support for people living in homelessness.
+More rigorous research is required.
+The decreased utilization rate during the COVID outbreak may indicate that more individuals are experiencing severe challenges, preventing them from accessing shelters.
+Furthermore, it is insufficient to comment on the current state of government support since this data only goes up to 2020.
+
+Understanding the development and importance of support services among people experiencing homelessness is essential.
+Moreover, a critical issue is how this support should be delivered.
+It is important to provide assistance without disrupting individuals' lives, for instance, by avoiding practices that displace or isolate them from their communities, such as relocating them to shelters far from their usual support systems (@boucher2022they).
+This is a long journey to go.
 

### 2024-09-27 paper/paper.qmd
fix typo

@@
 # Data {#sec-data}
-All data reviewed and analysis in this paper is the Daily Shelter Occupancy @Shelter.
-The data is essential for evaluating how shelters serve different populations (e.g., men, women, youth, families) and for analyzing the current shelter servise system over time, such as capacity shortfalls or surpluses.
-It provides inforamtion on all the active shelters exist in the City of Toronto area, collected in forms of four separate datasets corresponding to the years 2017, 2018, 2019, and 2020.
+All data reviewed and analyzed in this paper comes from the Daily Shelter Occupancy (@Shelter), on Open Data Toronto Portal @OpenDataToronto.
+This data is essential for evaluating how shelters serve various populations (e.g., men, women, youth, families) and for analyzing the shelter service system during and after the pandemic, including capacity shortfalls or surpluses.
+It provides information on all active shelters in the City of Toronto, collected in four separate datasets corresponding to the years 2017, 2018, 2019, and 2020.
 
 ## Overview {#sec-data-overview}
-Each datasets include various characteristics of the shelters.
-The data was sourced from an Open Data Toronto Portal @OpenDataToronto, with each row indicate a unique entry for a specific sector of specific shelter, on a specific date, and has Unique row identifier for Open Data database, "_id".
+Each dataset includes characteristics of the shelters.
+The data was sourced from the Open Data Toronto Portal @OpenDataToronto, with each row representing a unique entry for a specific sector of a specific shelter on a specific date.
+Each entry has a unique row identifier,  "_id", for the Open Data database.
+The collection process records information about the name of the non-profit organization responsible for the shelter, the name of the facility (e.g., hotel, residential building), and its capacity to accommodate homeless individual.
+Capacity is measured by the number of beds or mats/cots available.
+Data is collected at 4:00 AM each day to record the number of homeless clients occupying the shelters.
+This consistent method provides a accurate snapshot of shelter use across all organizations.
 
-The collection process records information about corresponding name of the non-profit entity that is responsible for the shelter, as well as the name of the facility (e.g.
-hotel, residence building), along with and their capacity to accommodate homeless clients.
-The Capacity is being measured as number of bed or a mat/cot available.
-Something will happen is that for the family sector, it is possible to exceed available capacity depending on the bed number, because family could be accommodated in a room with number beds smaller than number of people in their family.
-The data was collected every day, 4:00 AM, to record number of homeless clients occupying the shelters.
-This way to gather information about occupancy provides a consistent snapshot of shelter use across all organizations.
-
-Other similar datasets, especialy the ther dataset publish by Toronto Shelter & Support Services, were considered.
-However, they did not offer the cross-sector view of both occupancy and capacity needed for the focus of this analysis.
-The selected dataset allows for a broad comparison across time and sectors in different city, providing a fuller picture of trends within the shelter system.
+Other similar datasets, especially another one published by Toronto Shelter & Support Services, were considered; however, they did not provide the cross-sector view of both occupancy and capacity needed for this analysis.
+The selected dataset allows for broad comparisons across time (importantly covering the period of the pandemic outbreak) and sectors within different cities, providing a more comprehensive picture of trends within the shelter system.
 
@@
 
-For the purpose of this analysis, several features are chose to be particularly focused on.
-variable of interest including the the city (named "SHELTER_CITY" in the dataset) in which shelters are located; the date of data recorded("OCCUPANCY_DATE"); the sector("SECTOR") of clientele the shelters serve, for example men, women, youth, families, and even co-ed; the shelter's capacities("CAPACITY") and occupancy("OCCUPANCY") levels.
-These variables were chosen for their relevance in which is to investigate shelter occupancy and capacity across different cities and sectors, focusing on the City of Toronto from 2017 to 2020.
+This analysis focuses on several key features.
+The variables of interest include the city ("SHELTER_CITY") where the shelters are located, the date of data recording ("OCCUPANCY_DATE"), the sector ("SECTOR") of clientele served by the shelters (e.g., men, women, youth, families, and co-ed), as well as the shelter's capacity ("CAPACITY") and occupancy ("OCCUPANCY") levels.
+These variables were selected for their relevance in examining shelter occupancy and capacity across different cities and sectors, with a particular emphasis on the City of Toronto from 2017 to 2020.
 
-There are also seven other detailed feature in the datasets: "ORGANIZATION_NAME", "SHELTER_NAME", "SHELTER_ADDRESS", "SHELTER_PROVINCE", "SHELTER_POSTAL_CODE", "FACILITY_NAME", and "PROGRAM_NAME".
-Using R programming lanaguage @citeR, the `janitor`@R-janitor, `tidyverse` @R-tidyverse, and `dplyr` @R-dplyr pakages are used in data simulation, downloading, cleaning, and writting test.
-No new variables were created for this analysis, but the data was aggregated by grouping observations by city, date, and sector.
-This aggregation facilitated a more comprehensive comparison across cities and sector groups.
-A random sample of the cleaned data can be seen in @fig-shelter-sample.
+The dataset also includes seven additional detailed features: "ORGANIZATION_NAME", which is the registered name of the entity in charge; "SHELTER_NAME", the name of the shelter sit; "SHELTER_ADDRESS", the address of the shelter, "SHELTER_PROVINCE", which are all Ontario in this case; "SHELTER_POSTAL_CODE", the postal code of the shelter; "FACILITY_NAME", the name of the facilities taking in homeless clients; and "PROGRAM_NAME", which means the name of actual programs or services within the facility.
+The R programming language @citeR, the `janitor`@R-janitor, `tidyverse` @R-tidyverse, and `dplyr` @R-dplyr packages are used in data simulation, downloading, cleaning, and writing test.
+were utilized for data simulation, downloading, cleaning, and writing tests for data.
+No new variables were created for this analysis.
+The data was aggregated by grouping observations by city, date, and sector, enabling a more comprehensive comparison across cities and sector groups in the duration of time.
+A random sample of the cleaned data is presented in @fig-shelter-sample.
 ```{r}
@@
 ## Data Breakdown
-As shown in @fig-shelter-full-table, The four cities being observed in the dataset are Toronto, Etobicoke, North York, and Scarborough.
-The sectors recorded include Co-ed (mixture), Families, Men, Women, and Youth.
-Across all cities, record for Youth age group being presents.
-In fact, Youth is the only population in Etobicoke and North York.
-In Toronto, which has the most number of observation recorded, equal number of sectors are being observed, but how these people in distributed inthe total popluation are not clear.
-This will be further addressed in the following sections.
+As shown in @fig-shelter-full-table, the data includes observations from four cities: Toronto, Etobicoke, North York, and Scarborough.
+The recorded sectors encompass Co-ed (mixed), Families, Men, Women, and Youth.
+Notably, the Youth age group is represented across all cities, as well as being the only population recorded in Etobicoke and North York.
+Toronto, with the highest number of observations, includes an equal number of sectors, but the distribution of individuals within the total population is unclear.
+This aspect will be addressed in the following sections.
+
 ```{r}
@@
 
-The following table @fig-shelter-diff-city provides a summary of the average, maximum, and minimum occupancy, as well as capacity metrics for each city.
-Toronto has most amount of shelter avaliable and also has most people occuupaying in.
-The Maximum occupany of Toronto in a day, combined all sectors, from 2017 to 2020,is 6803.
-Wheras Etobicoke only has 53 people occupanying.
-The fact that Etotobike has only hoemless people in the group of Youth recorded could explain alittle bit.
-But, the de=ifference still strong enough to see that the homeless population might be significant larger in Toronto compared to aother cities.
+The following table @fig-shelter-diff-city summarizes the average, maximum, and minimum occupancy and capacity quantity for each city.
+Toronto has the highest number of shelters available by looking at the capacity; as well as the with greatest amount of individuals utilizing them.
+The maximum occupancy in Toronto, across all sectors from 2017 to 2020, reached 6,803 people, while Etobicoke had only 53 individuals occupying shelters.
+The fact that Etobicoke recorded homeless individuals solely within the Youth group provides some explanation, but the significant difference still implies that the homeless population in Toronto is much larger as compared to other cities.
 ```{r}
@@
 ```
-The relastion ship of two key feature, occupancy and capacity, are essential for understaidng current shelter servise system.
-The relashipship is reflected in @fig-occupancy-capacity-relashionship.
-Occupany and capacity are greatly follwing a positive correlation, indicating that most there aren't much over-investment to the shelter system, nor heavily over-filled shelter.
-But there are noticible deviation from the perfect correlation to above, these are suggecting there are cases where occupany is higher than capacity, suggesting occupantee may living in a overly paked places.
-More will be dicussed in  @sec-results, including other learning on the shelter servise like thier trend, and how these shelter information possiblly reflect the homeless.
+The relationship between two key features, occupancy and capacity, is essential for understanding the shelter service system for the period 2017 to 2020, as well as proposing possible improvements for the current system.
+This relationship is illustrated in @fig-occupancy-capacity-relationship.
+Occupancy and capacity show a good following to positive correlation, indicating that there is not much over-investment in the shelter system, nor are shelters heavily over-occupied.
+However, few noticeable deviations from perfect correlation suggest presence where occupancy exceeds capacity, indicating that some individuals in homeless condition may be accomading in overcrowded shelters Further discussions on trends in the shelter service system and how this data reflects the homeless population will be presented in @sec-results.
+
 ```{r}
@@
 # Results {#sec-results}
-Through grpahfical study of the datset, some usful information are found and the result will be dicussed in this section.
+Through a graphical and numerical analysis of the dataset, some valuable insights into shelter system usage are uncovered.
+By visualizing the trends over time and studying data across different demographics and time, we can try to figure out how various factors influence the utilization and performance of shelter services.
+This section will delve into the findings, highlighting patterns and variation that emerged from the data.
+Additionally, we will discuss the implications of these results for working to address the living needs of homeless populations.
 

### 2024-09-27 paper/paper.qmd
changes in cross-reference

@@
 ---
-title: "Marriage Data analysis"
-subtitle: "STA304 WEEK 3"
+title: "City of Toronto's Response to Homelessness during the COVID-19 Pandemic"
+subtitle: "Analyzing Shelter Occupancy, Capacity, and Adaptability in the City of Toronto"
 author: 
@@
 date-format: long
-abstract: "This paper investigates the occupancy of shelters in Toronto from 2017 to 2020, focusing on capacity and usage across different shelter sectors.
-By analyzing the data, we explore how shelter demand {exceeded available resources in certain sectors.
-This research highlights significant challenges faced by the shelter system, providing insights into the strain on resources and potential gaps in support for the homeless population}.
-These findings are crucial for informing policies and improving resource allocation to better address homelessness in Toronto."
+abstract: "This paper studies the trends in shelter occupancy across Toronto from 2017 to 2020, including the impact of the COVID-19 pandemic on the homeless population.
+Utilizing data sourced from the Open Data Toronto portal, patterns of shelter utilization among various demographics are analyzed.
+The findings reveal a significant increase in shelter occupancy during of outbreak of the pandemic.
+The data indicates that the local shelters maintained effective utilization rates and responded to the needs by increasing capacity.
+The paper highlights key insights into the adaptability of the shelter system in meeting the necessities of the homeless population and potentially contribute to the effectiveness of local government's responses to the issue regards homelessness."
 format: pdf
+toc: true
 number-sections: true
@@
 
-This paper analyzes shelter occupancy data from 2017 to 2020 in the City of Toronto, sourced from the Open Data Toronto portal (@OepnDataToronto).
+This paper analyzes shelter occupancy data from 2017 to 2020 in the City of Toronto, sourced from the Open Data Toronto Portal @OpenDataToronto.
 By examining occupancy trends during this period, particularly during the COVID-19 pandemic, we aim to evaluate how effectively the city's shelters met the increased demand.
@@
 
-The remainder of this paper is presented in sections: @sec-data :Data, @sec-results :Results, @sec-discussion :Discussion, and @sec-weakness :Weaknesses and Next Steps.
+The remainder of this paper is presented in sections: @sec-data :Data, @sec-results :Results, @sec-discussion :Discussion, and @sec-limitation :Limitation and Next Steps.
 The data section introduces the dataset used for analysis, explaining its source and the context that shaped its collection.
@@
 # Data {#sec-data}
-All data reviewed and analyzed in this paper comes from the Daily Shelter Occupancy (@Shelter), on Open Data Toronto Portal @OpenDataToronto.
+All data reviewed and analyzed in this paper comes from the Daily Shelter Occupancy, by @Shelter, on Open Data Toronto Portal @OpenDataToronto.
 This data is essential for evaluating how shelters serve various populations (e.g., men, women, youth, families) and for analyzing the shelter service system during and after the pandemic, including capacity shortfalls or surpluses.
@@
 The relationship between two key features, occupancy and capacity, is essential for understanding the shelter service system for the period 2017 to 2020, as well as proposing possible improvements for the current system.
-This relationship is illustrated in @fig-occupancy-capacity-relationship.
+This relationship is illustrated by @fig-relashionship.
 Occupancy and capacity show a good following to positive correlation, indicating that there is not much over-investment in the shelter system, nor are shelters heavily over-occupied.
@@
 ```{r}
-#| label: fig-occupancy-capacity-relashionship
+#| label: fig-relashionship
 #| fig-cap: Relationship Between Total Occupancy and Total Capacity in Shelter of the City of Toronto
@@
   geom_smooth(method = "lm", se = FALSE) +
-  labs(title = "Relationship Between Total Occupancy and Total Capacity in Shelter of the City of Toronto",
+  labs(title = "Relationship Between Occupancy and Capacity in Shelter",
        x = "Total Capacity",
@@
 
-## Shelter Occupancy Trend over Time
+## Shelter Occupancy Trend Over Time
 The figure @fig-shelter-over-time depicts the trend of homeless people occupying shelters in each city over time.
@@
 Especially, there is an rising trend in Scarborough.
-This rise coincides with the outbreak of COVID-19, as noted in the "About Daily Shelter Occupancy" section in the data website @ShelterThe.
-significant decrease in occupancy from mid-2020 across all cities further supports this correlation, suggesting the pandemic had a direct impact on shelter use.
+This rise coincides with the outbreak of COVID-19, as noted in the "About Daily Shelter Occupancy" section in the data website @Shelter.
+The decrease in occupancy from mid-2020 across all cities further supports this correlation, suggesting the pandemic had a direct impact on shelter use.
 ```{r}
@@
 ## Over Capacity Cases
-The relationship between occupancy and capacity over the four years (@fig-occupancy-capacity-relashionship) reveals instances where shelter capacity was exceeded, as we discussed in the Data section (@sec-data).
+The relationship between occupancy and capacity over the four years (@fig-relashionship) reveals instances where shelter capacity was exceeded, as we discussed in the Data section (@sec-data).
 These cases where capacity is exceeded (when $occupancy > capacity$) are important to study when considering improvement shelter system improvement.
@@
 
-## Weaknesses and next steps {#sec-weakness}
+# Limitation and Next Steps {#sec-limitation}
 
@@
 
+\newpage
+
 # References

### 2024-09-28 paper/paper.qmd
%>% to |>

@@
 # Count the number of observations by city and sector
-city_sector_breakdown <- shelter_data %>%
-  group_by(shelter_city, sector) %>%
-  count() %>%
+city_sector_breakdown <- shelter_data |>
+  group_by(shelter_city, sector) |>
+  count() |>
   spread(key = sector, value = n, fill = 0)
@@
 # Display the table with correct formatting
-city_sector_breakdown %>%
+city_sector_breakdown |>
   kable(caption = "Number of Observations by City and Sector")
@@
 
-toronto_data <- shelter_data %>% 
-  filter(shelter_city == "Toronto") %>% 
-  group_by(occupancy_date) %>%
+toronto_data <- shelter_data |> 
+  filter(shelter_city == "Toronto") |> 
+  group_by(occupancy_date) |>
   summarise(
@@
 
-north_york_data <- shelter_data %>% 
-  filter(shelter_city == "North York") %>%
-  group_by(occupancy_date) %>%
+north_york_data <- shelter_data |> 
+  filter(shelter_city == "North York") |>
+  group_by(occupancy_date) |>
   summarise(
@@
 
-scarborough_data <- shelter_data %>% 
-  filter(shelter_city == "Scarborough")%>%
-  group_by(occupancy_date) %>%
+scarborough_data <- shelter_data |> 
+  filter(shelter_city == "Scarborough")|>
+  group_by(occupancy_date) |>
   summarise(
@@
 
-etobicoke_data <- shelter_data %>% 
-  filter(shelter_city == "Etobicoke") %>%
-  group_by(occupancy_date) %>%
+etobicoke_data <- shelter_data |> 
+  filter(shelter_city == "Etobicoke") |>
+  group_by(occupancy_date) |>
   summarise(
@@
 # Summary statistics for each city
-toronto_summary <- toronto_data %>%
+toronto_summary <- toronto_data |>
   summarise(
@@
 
-north_york_summary <- north_york_data %>%
+north_york_summary <- north_york_data |>
   summarise(
@@
 
-scarborough_summary <- scarborough_data %>%
+scarborough_summary <- scarborough_data |>
   summarise(
@@
 
-etobicoke_summary <- etobicoke_data %>%
+etobicoke_summary <- etobicoke_data |>
   summarise(
@@
 combined_summary$city <- city
-combined_summary <- combined_summary %>%
+combined_summary <- combined_summary |>
   select(city, everything())
@@
 # Create individual plots for each city
-toronto_plot <- ggplot(toronto_data %>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+toronto_plot <- ggplot(toronto_data |> slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
   geom_line(color = "blue") +
@@
 
-north_york_plot <- ggplot(north_york_data%>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+north_york_plot <- ggplot(north_york_data|> slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
   geom_line(color = "green") +
@@
 
-scarborough_plot <- ggplot(scarborough_data%>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+scarborough_plot <- ggplot(scarborough_data|> slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
   geom_line(color = "red") +
@@
 
-etobicoke_plot <- ggplot(etobicoke_data%>% slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
+etobicoke_plot <- ggplot(etobicoke_data|> slice(seq(1, n(), by = 50)), aes(x = occupancy_date, y = total_occupancy)) +
   geom_line(color = "orange") +
@@
 # Calculate utilization rate by city
-toronto_data <- toronto_data %>%
+toronto_data <- toronto_data |>
   mutate(utilization_rate = total_occupancy / total_capacity)
 
-north_york_data <- north_york_data %>%
+north_york_data <- north_york_data |>
   mutate(utilization_rate = total_occupancy / total_capacity)
 
-scarborough_data <- scarborough_data %>%
+scarborough_data <- scarborough_data |>
   mutate(utilization_rate = total_occupancy / total_capacity)
 
-etobicoke_data <- etobicoke_data %>%
+etobicoke_data <- etobicoke_data |>
   mutate(utilization_rate = total_occupancy / total_capacity)
@@
 combined_data <- bind_rows(
-  toronto_data %>% mutate(shelter_city = "Toronto"),
-  north_york_data %>% mutate(shelter_city = "North York"),
-  scarborough_data %>% mutate(shelter_city = "Scarborough"),
-  etobicoke_data %>% mutate(shelter_city = "Etobicoke")
+  toronto_data |> mutate(shelter_city = "Toronto"),
+  north_york_data |> mutate(shelter_city = "North York"),
+  scarborough_data |> mutate(shelter_city = "Scarborough"),
+  etobicoke_data |> mutate(shelter_city = "Etobicoke")
 )
@@
 # Extract year from occupancy_date
-combined_data <- combined_data %>%
+combined_data <- combined_data |>
   mutate(year = year(occupancy_date),
@@
 # Have data into seasons
-combined_data <- combined_data %>%
+combined_data <- combined_data |>
   mutate(season_year = factor(paste(season, year), 
@@
 # Calculate average utilization rate
-annual_utilization <- combined_data %>%
-  group_by(season_year, shelter_city) %>%
+annual_utilization <- combined_data |>
+  group_by(season_year, shelter_city) |>
   summarise(avg_utilization_rate = mean(utilization_rate, na.rm = TRUE), .groups = 'drop')
@@
 toronto_plot <- ggplot(
-  toronto_data %>% slice(seq(1, n(), by = 100)), 
+  toronto_data |> slice(seq(1, n(), by = 100)), 
                          aes(x = occupancy_date, y = total_capacity)) +
@@
 north_york_plot <- ggplot(
-  north_york_data %>% slice(seq(1, n(), by = 100)), 
+  north_york_data |> slice(seq(1, n(), by = 100)), 
   aes(x = occupancy_date, y = total_capacity)) +
@@
 scarborough_plot <- ggplot(
-  scarborough_data %>% slice(seq(1, n(), by = 100)), 
+  scarborough_data |> slice(seq(1, n(), by = 100)), 
   aes(x = occupancy_date, y = total_capacity)) +
@@
 etobicoke_plot <- ggplot(
-  etobicoke_data %>% slice(seq(1, n(), by = 100)), 
+  etobicoke_data |> slice(seq(1, n(), by = 100)), 
   aes(x = occupancy_date, y = total_capacity)) +
@@
 # Filter for overcrowded data
-overcrowded_data <- shelter_data %>%
+overcrowded_data <- shelter_data |>
   filter(total_occupancy > total_capacity)
@@
 # Create a frequency table including all cities and sectors
-frequency_table <- overcrowded_data %>%
-  group_by(shelter_city, sector) %>%
-  summarise(count = n(), .groups = 'drop') %>%
-  complete(shelter_city, sector, fill = list(count = 0)) %>%
+frequency_table <- overcrowded_data |>
+  group_by(shelter_city, sector) |>
+  summarise(count = n(), .groups = 'drop') |>
+  complete(shelter_city, sector, fill = list(count = 0)) |>
   pivot_wider(names_from = sector, values_from = count)
@@
 # Create a frequency table including all cities and sectors
-frequency_table <- overcrowded_data %>%
-  group_by(shelter_city, sector) %>%
-  summarise(count = n(), .groups = 'drop') %>%
-  right_join(all_combinations, by = c("shelter_city", "sector")) %>%
-  replace_na(list(count = 0)) %>%
+frequency_table <- overcrowded_data |>
+  group_by(shelter_city, sector) |>
+  summarise(count = n(), .groups = 'drop') |>
+  right_join(all_combinations, by = c("shelter_city", "sector")) |>
+  replace_na(list(count = 0)) |>
   pivot_wider(names_from = sector, values_from = count, values_fill = 0)
@@
 # View the frequency table with knitr
-frequency_table %>%
+frequency_table |>
   kable(caption = "Overcrowded Cases by City and Sector")
